Modern Graph Generators: A Survey

### 2018-10-20 comparison.tex
Minor corrections

In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first provide an overview of the approaches used in related work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy would differ as well.

@@

\begin{itemize}
\item Characteristics of the \textbf{domain} -- its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample''),
\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Upd.''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key \textbf{configuration} options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
    \item \textit{output format} (column ``Output'') of the produced graph, and
    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
  \end{itemize}
\end{itemize}

@@

               & \textbf{Upd.}

@@

  & Preferential attachment & -- & -- & Y & N & Y & power-law & edge-list &  N  \\

@@

   & R-MAT & -- & -- & Y & N & Y & power-law & edge-list &  N  \\

@@

  & GraphGen & -- & -- & Y & N & Y& user-defined  & node/edge-list & N   \\

@@

\paragraph{Number of Generators, Size and Output Format of the Data}
As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic. None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale. On the other hand, Linked Open Data (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.

@@

If we consider the features of the particular domain of the generators, in most cases it is expectably fixed. It is the simplest option, but it does mean that the generator is simple too -- it can still focus on other complex aspects of the output. The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas. They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP or DBpedia). Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven/pattern-driven domain or a domain extracted from sample data.

@@

Generators for community detection aim, in general, at creating graphs with a
more realistic strcture (graphs with communities of nodes where the density of
edges is larger internally than externally). Even though these generators are,
in general used to test community detection algorithms (they generate also the
expected communities in the graph), some studies also use them for general graph
purposes or to test graph analytics algorithms besides community detection.

>>>>

In order to provide the reader with a quick preview of the generators and thus to enable finding the target solutions easily, we start the survey with a  classification and comparative study of the existing tools. In general, there are various ways to classify them. We first provide an overview of the approaches used in related work after which we then introduce our approach. As mentioned in the Introduction, since this survey is unique especially in terms of scope, our classification and comparative strategy differs as well.

@@

\begin{itemize}
\item Characteristics of the \textbf{domain} -- its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample''),
\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Update''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key \textbf{configuration} options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
    \item \textit{output format} (column ``Output'') of the produced graph, and
    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
  \end{itemize}
\end{itemize}

@@

               & \textbf{Update}

@@

  & Preferential attachment & -- & -- & N & N & Y & power-law & edge-list &  N  \\

@@

   & R-MAT & -- & -- & N & N & Y & power-law & edge-list &  N  \\

@@

  & GraphGen & -- & -- & N & N & Y& user-defined  & node/edge-list & N   \\

@@

\paragraph{Number of Generators, Size and Output Format of the Data}
As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic. None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale. On the other hand, the \emph{Linked Open Data} (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.

@@

If we consider the features of the particular domain of the generators, in most cases it is expectably fixed. It is the simplest option, but it does mean that the generator is simple too -- it can still focus on other complex aspects of the output. The particular target (in case of fixed) or sample (in case of schema-driven or extracted) domains do not provide very rich areas. They either correspond to the respective application domains (like in the case of social networks), or they are based on well-known and commonly used data sets (such as, e.g., DBLP~\cite{dblp} or DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}). Except for general graphs without any domain, in all other cases we can find a flexible representative with schema-driven/pattern-driven domain or a domain extracted from sample data.

@@

Generators for community detection aim, in general, at creating graphs with a
more realistic structure (graphs with communities of nodes where the density of
edges is larger internally than externally). Even though these generators are,
in general, used to test community detection algorithms (they generate also the
expected communities in the graph), some studies also use them for general graph
purposes or to test graph analytics algorithms besides community detection.

### 2018-10-20 generators_LinkedData.tex
Minor corrections

\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP~\cite{dblp} as a domain for the dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated documents mirror key characteristics and distributions found in the original DBLP database. The data mimics natural correlations between entities, such as power law distributions (found in the citation system or the distribution of publications among authors) and limited growth curves (e.g., the increasing number of venues and publications over time). All random functions of the generator base on a fixed seed which makes data generation deterministic. SP$^2$Bench is accompanied by 12 queries covering different operator constellations, RDF access paths, typical RDF constructs etc.

@@

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia~\cite{Bizer:2009:DCP:1640541.1640848}, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$. The type system is extracted from the data set by looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness. In addition they show that structuredness and size mutually influence each other.

>>>>

\paragraph{SP$^2$Bench} The SP$^2$Bench\footnote{\url{http://dbis.informatik.uni-freiburg.de/forschung/projekte/SP2B/}} is a language-specific benchmark~\cite{Schmidt2010} which uses the DBLP as a domain for the dataset. %, so the types involve Person, Inproceedings, Article etc.
The generated documents mirror key characteristics and distributions found in the original DBLP database. The data mimics natural correlations between entities, such as power law distributions (found in the citation system or the distribution of publications among authors) and limited growth curves (e.g., the increasing number of venues and publications over time). All random functions of the generator base on a fixed seed which makes data generation deterministic. SP$^2$Bench is accompanied by 12 queries covering different operator constellations, RDF access paths, typical RDF constructs etc.

@@

\paragraph{Data Coherence}  A comparison of 4 RDF benchmarks (namely TPC-H~\cite{TPC-H} data expressed in RDF, LUBM, BSBM, and SP$^2$Bench) and 6 real-wold data sets (such as, e.g.,  DBpedia, the Barton Libraries Dataset~\cite{barton-benchmark} or
WordNet~\cite{Miller:1995:WLD:219717.219748}) has been reported by~\cite{Duan:2011:AOC:1989323.1989340}. The authors focus mainly on the  \emph{structuredness} (\emph{coherence}) of each benchmark dataset claiming that a primitive metric (e.g., the number of triples or the average in/outdegree) quantifies only some specific aspect of each dataset. The level of structuredness of a dataset $D$ with respect to a type $T$ is determined by how well the instance data in $D$ conforms to type $T$. The type system is extracted from the data set by looking for triples whose property is \texttt{http://www.w3.org/1999/02/22-rdf-syntax-ns\#type} and extracting type $T$ from their object. Properties of $T$ are determined as the union of all the properties that the instances of type $T$ have. The structuredness is then expressed as a weighted sum of share of set properties of each type, whereas higher weights are assigned to types with more instances. The authors show that the structuredness of the chosen benchmarks is fixed, whereas real-world RDF datasets lie in currently untested parts of the spectrum. As a consequence, they introduce a new benchmark that accepts as input any dataset along with a desired level of structuredness and size (smaller than the size of the original data), and uses the input dataset as a seed to produce a subset of the original data with the indicated size and structuredness. In addition they show that structuredness and size mutually influence each other.
